\documentclass{diaryformat}

\projectName{Dragon-Fly: Vehicle Survlience system}
\guideName{Dr. Rafeeque P.C}

\addGrpMember{Abhinand C}{05}
\addGrpMember{Edwin Jose George}{27}
\addGrpMember{Lavanya E.V}{32}
\addGrpMember{Shilpa Suresh}{50}

\begin{document}

\begin{workDone}{3 March}{14 March 2022}
	\begin{itemize}
		\item Backend - Developed boilerplate code. Developed intermediate data representation format.
		\item Experimented with OpenCV Haar Model. Developed sample object detection for car and bus. Forked the repo of Aman-Preeth-Singh-Gulati/vehicle-count-detect
		\item Experimented with tensorflow object detection model. Forked and ran basic detection mentioned on tutorials.
		\begin{itemize}
			\item Ran cat-dog classification
			\item Got an understanding of intermediate layer output and working of CNN
		\end{itemize}
		\item Found SOTA yolo model and Mask-RCNN explanations. Found few datasets sources (eg: NVIDIA AI city challenge, tensorflow Datasets, Kaggle Datasets etc)
		\item Design of MockServer. Developed python code for video stream handler to extract video.
		\item Conducted research on datasets, pre-trained repos. Few notable repos at hand:
		\begin{itemize}
			\item tensorflow Object counting API
			\item vehicle\_reID-Collection
			\item https://github.com/cw1204772/AIC2018\_iamai
			\item https://github.com/tensorflow/models/tree/master/official
		\end{itemize}
		\item Tested live camera infrastructure and obtained access to camera and NVR infrastructure
	\end{itemize}

\end{workDone}

\end{document}
