%==================================acknowledgement.tex=============================
\chapter*{Acknowledgment}%
\addcontentsline{toc}{chapter}{Acknowledgement}%

%\newenvironment{acknowledgement}

\begin{spacing}{1.45}
	\par We take this opportunity to express our deepest sense of gratitude and sincere thanks to everyone who helped us to complete this work successfully. We express our sincere thanks to \hod, Head of Department, \dept, \college\hspace*{2pt} for providing  us with all the necessary facilities and support.\par
	
	We would like to express our sincere gratitude to the \projcordinatorA, department of \dept, \college \space for the support and co-operation.
	
	We would like to place on record our sincere gratitude to our project guide \guide, \guidedes, \dept, \college  %and our external guide \guideext,\hspace*{2pt}\guideextdes, \hspace*{2pt} \guideextorg   
	\space for the guidance and mentorship throughout this work, providing with valuable timely suggestions and corrections.
	
	We would also like to extend our gratitude to Dr. P Sooraj, Mechanical Dept. for inspiring us with the great idea and vision on our work. Thanks to Bineesh K.B sir, Dept. of CSE, for supporting us with technical resources. Thanks to Prof. Asjad Nabeel P for all those tips and tricks. Thanks to all the teaching/supporting staffs of Govt. College of Engineering Kannur for supporting and motivating us through the journey.
	
	Finally I thank my family, and friends who contributed to the successful fulfillment of this project work.
	
	\vfill
	\begin{flushright}
		\textbf{\studentA}\\
		\textbf{\studentB}\\
		\textbf{\studentC}\\
		\textbf{\studentD}\\
	\end{flushright}
\end{spacing}

\thispagestyle{plain}
