\chapter{Conclusions and Future Scope}\section{Conclusion}The project is developed using the existing technology and methods. This project extends the functionality of camera network offered by CICET. The footage are captured and processed by AI services. YOLOv4 model computes the bounding box along with the class confidence. DeepSORT uses the deep matrix to conduct multi-tracking in multiple objects. Upon the user query, the most relevant detections are provides, which the user can visually verify. This leads to the development of route parsed by the target vehicle. This project thus helps fast tracking of vehicles. The project can be considered as one of candidates for Open AI challenge proposed by NVIDIA. \section{Future Scope}Various levels of improvement can be done, specially in AI domain. Since False Positive do not have heavy impact on the problem domain, a fair trade-off can be applied between the speed and accuracy of the model. Heuristics can be applied after conducting the deeper analysis of the traffic pattern. Various development of PP-YOLO, a PyTorch implementation of YOLO model, is gaining popularity. A new framework called PaddlePaddle \cite{paddlepaddle} is being developed aiming distributed processing, which can significantly increase the processing speed. Various methods are being proposed in PaddlePaddle that significantly reduces the complexity of several algorithms, making real-time application more realizable. Below are some of the pointer that can further enhance the functionality of the project:\begin{itemize}	\item Usage of higher resolution camera can better extract the unique feature of vehicles. Cameras can be placed under a bright light source enabling better detection at night.	\item Integration of license plate detection and Motor Vehicle Department can be used to reverse map the vehicle description, in search of forged vehicle registration.	\item Train the model in varying weather condition such as sunny, cloudy, rainy etc. Target classes can be increased to detect sub-category of vehicles.	\item Tighter integration of YOLO model and DeepSORT can reduce redundant extraction and processing of feature vectors.	\item Current route generation requires visual inspection, which can be replaced by successful implementation of Siamese Network.	\item Mapping between camera needs to be improved for better route estimation.	\item Use of elastic search at user interface for interaction and extraction of feature description.	\item Use of PP-YOLO with PaddlePaddle framework can boost the overall performance of the distributed system.\end{itemize}